%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.8in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Brandon Robinson} \\ \vspace{1pt}
    \small 470-208-0415 $|$ \href{mailto:1802brad@gmail.com}{\underline{1802brad@gmail.com}} $|$ 
    \href{https://linkedin.com/in/bran-robisnon}{\underline{https://www.linkedin.com/in/bran-robinson/}} $|$
    \href{https://github.com/btylrob}{\underline{github.com/Btylrob}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Florida International University}{Miami, FL}
    {Bachelor of Arts in Computer Science, Minor in Statistics}{Aug. 2025 -- Exp. 2027}
    \resumeItemListStart
      \resumeItem{Dean’s List; Member of CodeCrunch and InTech student-led clubs}
      \resumeItem{1st Place, Broward College Math Awareness Competition}
      \resumeItem{Relevant Coursework: Discrete Math, Data Science, SQL, Programming I \& II}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages:} Python, C++, Bash/Shell Scripting, SQL\\
      \textbf{Technologies:} Docker, Wireshark, Jenkins, Git, AWS, Cassandra, Ansible \\
      \textbf{Concepts:} OS Fundamentals, Discrete Math, CI/CD, Linux Architecture, network protocols (TCP, UDP)
    }}
  \end{itemize}



%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Altius}{July 2025 -- October 2025}
      {Software Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and deployed scalable full-stack applications using Flutter, TypeScript, and Firebase, supporting hundreds of users with real-time preference synchronization.}
        \resumeItem{Built robust backend services in TypeScript/JavaScript, architecting APIs to efficiently manage and query structured customer data across Firebase Firestore and Pinecone vector databases.}
        \resumeItem{Developed and maintained CI/CD pipelines via GitHub Actions, automating test, build, and deployment workflows to ensure fast, zero-downtime releases across multiple environments.}
        \resumeItem{Increased student and recruiter onboarding speed by automating account provisioning, streamlining UI flows, and integrating real-time preference management.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Market Data Ingestion Pipeline} $|$ \emph{Python, ZeroMQ, Cassandra, Docker}}{}
\resumeItemListStart
  \resumeItem{Implemented an event driven ingestion service to capture and normalize high-frequency cryptocurrency market headlines from multiple data streams with sub 10ms processing latency.}
  \resumeItem{Designed a concurrent, backpressure-aware pipeline using asyncio and ZeroMQ to ensure deterministic performance under burst loads.}
  \resumeItem{Persisted normalized and timestamped events in Apache Cassandra for scalable, low-latency querying of historical and real-time data.}
  \resumeItem{Developed real-time momentum and frequency shift detectors to surface early market-moving events.}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{Low-Latency Stock Time-Series Database} $|$ \emph{C, POSIX, Lock-Free Concurrency}}{}
\resumeItemListStart
  \resumeItem{Implemented a custom time-series database in C purpose-built for ingesting high-frequency market data with sub-millisecond latency, sustaining millions of ticks per trading session without loss.}
  \resumeItem{Designed a memory-mapped, append-only storage engine with bespoke time-window indexing, enabling constant-time retrieval of tick and OHLC data across arbitrary intervals.}
  \resumeItem{Built a lock-free, multi-threaded ingestion pipeline leveraging ring buffers and fine-grained concurrency primitives for deterministic performance under burst loads.}
  \resumeItem{Optimized cache locality, I/O throughput, and branch prediction using Linux perf and CPU profiling tools, achieving a 3× throughput gain over baseline implementations.}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{FPGA + Server Hybrid Low-Latency Market Data Pipeline} $|$ \emph{Verilog, PCIe DMA, Linux, Lock-Free Concurrency}}{}
\resumeItemListStart
  \resumeItem{Engineered an FPGA-based UDP multicast parser with nanosecond-precision hardware timestamping and symbol-level filtering, achieving deterministic packet handling at 10Gbps line rate.}
  \resumeItem{Designed and implemented a PCIe DMA engine to transfer normalized market data from FPGA to server memory with zero-copy, bypassing the kernel network stack.}
  \resumeItem{Built a lock-free, multi-threaded feed handler on Linux to consume FPGA output from shared memory, perform real-time order book aggregation, and measure tick-to-trade latency.}
  \resumeItem{Benchmarked and tuned PCIe throughput, cache locality, and NIC offloading to achieve sub-1µs end-to-end latency under sustained market burst conditions.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\end{document}ument}
